\section{Presentations}

\underline{Oral Presentations}:
\orderedouterlist{
\entry{\textbf{Caruso*, K. E.}, Madden, M., Payne, S., Rock, M., and A. Siddhi. (2023). Spatial ecological modeling of suitable habitat and forecasted land cover change using remote sensing data to identify at-risk populations of \textit{Dionaea muscipula} (Venus flytrap) and inform species conservation efforts. \textit{Annual Meeting, American Geophysical Union:} 11–15 December 2023, San Francisco, CA. {\hfill| \small *Presenter}}

\entry{Allsbrook, K., Burke, S., \textbf{Caruso*, K. E.}, Childs-Gleason, L., Clayton, A., and K. Ross. (2023). 25 Years of the NASA DEVELOP Experiential Learning Model. \textit{Annual Meeting, American Geophysical Union:} 11–15 December 2023, San Francisco, CA. {\hfill| \small *Presenter}}

\entry{\textbf{Caruso, K. E.}, Lampley*, J., Rock, M., Siddhi, A., Zhu, S., Randall, J. L., Waitt, D., Weakley, A., Payne, S., and M. Madden. (2022). GIS spatial analysis and habitat suitability modeling using remote sensing data to help identify at-risk populations of US Carolina Coastal Plain endemic Venus flytrap (\textit{Dionaea muscipula}). \textit{Annual Meeting, Botanical Society of America:} 24–27 July 2022, Anchorage, AK. {\hfill \small | *Presenter}}

\entry{\textbf{Caruso*, K. E.}, and J. L. Horton. (2020). Assessing the effect of eastern hemlock decline from hemlock woolly adelgid infestation on mycorrhizal fungi. \textit{UNC Asheville 2020 Spring Undergraduate Research Symposium:} 21 April 2020, Asheville, NC. {\hfill \small | *Presenter}}

\entry{\textbf{Caruso*, K. E.} (2019). Lessons in Leaves: Learning from Plants through Scientific and Contemplative Practice. \textit{2019 McCullough Fellowship Annual Luncheon:} 4 December 2019, Asheville, NC. {\hfill| \small *Presenter}}
}

\underline{Poster Presentations}:
\orderedouterlist{
\entry{\textbf{Caruso*, K. E.}, Rock, M., Siddhi, A., Payne, S., and M. Madden. (2024). Informing \textit{Dionaea muscipula} (Venus flytrap) Conservation through Habitat Modeling and Forecasted Land Cover Change. \textit{oSTEM 14th Annual Conference:} 17–20 October 2024, Portland, OR. {\hfill| \small *Presenter}}

\entry{Bolinger, G., \textbf{Caruso, K. E.}, Monteiro, T., Sgan*, A., Villalobos-Heredia, C., West, T., and M. Woloszyn. (2023). Utilizing NASA Earth observation data to monitor trends in air quality during a drought case study to improve public health response to drought threats. \textit{American Geophysical Union Annual Meeting:} 11–15 December 2023, San Francisco, CA. {\hfill| \small *Presenter}}

\entry{\textbf{Caruso*, K. E.}, and J. R. Ward. (2020). Factors Contributing to Reproductive Success and Failure in Virginia Spiraea (\textit{Spiraea virginiana}), a Federally Threatened Shrub. \textit{UNC Asheville 2020 Spring Undergraduate Research Symposium:} 21 April 2020, Asheville, NC. {\hfill \small | *Presenter}}

\entry{\textbf{Caruso*, K. E.}, Kranyik, J., and J. R. Ward. (2020). Factors contributing to reproductive success and failure in Virginia spiraea (\textit{Spiraea virginiana}), a federally threatened shrub. \textit{81st Annual Meeting, Association of Southeastern Biologists:} 25–28 March 2020, Jacksonville, FL. {\hfill \small | *Presenter, conference canceled following abstract acceptance due to COVID-19 pandemic}}

\entry{\textbf{Caruso*, K. E.}, Horton, J. L., and A. A. Hove. (2020). Assessing the effect of eastern hemlock decline from hemlock woolly adelgid infestation on mycorrhizal fungi. \textit{81st Annual Meeting, Association of Southeastern Biologists:} 25–28 March 2020, Jacksonville, FL. {\hfill \small | *Presenter, conference canceled following abstract acceptance due to COVID-19 pandemic}}
}

\underline{Invited Talk}:
\orderedouterlist{

\entry{\textbf{Caruso*, K. E.} (2023). Highlights from NASA Capacity Building: DEVELOP. \textit{Health and Air Quality Applications Program Review 2023:} 29–30 March 2023, Asheville, NC. {\hfill| \small *Presenter}}

}