\section{Research Projects}

% \underline{NASA DEVELOP Projects}:
\compactouterlist{

\entrymiddle[\textbullet]
{Biomaterials for Stabilizing Defense Materials in Arctic Environments}{\textit{Montana State University}}{Sept. 2024 \textendash ~\textit{Present}}

\entrymiddle[\textbullet]
{Measuring Crop Yields in Northern Brazil During El Niño Conditions to Evaluate Trends in Agricultural Production and Support Crop Forecasting}{\textit{NOAA National Centers for Environmental Information}}{Jan. \textendash ~March 2024}

\entrymiddle[\textbullet]
{Multi-Hazard Approach to Mapping Flood Susceptibility and Vulnerability in Kentucky}{\textit{NOAA National Centers for Environmental Information}}{Jan. \textendash ~March 2024}

\entrymiddle[\textbullet]
{Methods for Monitoring Rhode Island Habitats: Contributing to a Framework for Targeted Conservation and Management}{\textit{NOAA National Centers for Environmental Information}}{Jan. \textendash ~March 2024}

\entrymiddle[\textbullet]
{Monitoring Trends in Air Quality During a Drought Case Study to Improve Public Health Response to Drought Threats}{\textit{NOAA National Centers for Environmental Information}}{June \textendash ~Aug. 2023}

\entrymiddle[\textbullet]
{Using Earth Observations to Evaluate Snow Variability through a Climatological Analysis to Support Ecological Monitoring in Northeast Alaska}{\textit{NOAA National Centers for Environmental Information}}{Jan. \textendash ~March 2023}

\entrymiddle[\textbullet]
{Evaluating the Role of Soil Moisture in Determining Vegetation Health, Fuel Loads, and Wildfires in the Gatlinburg and Beatty Wildfires}{\textit{NOAA National Centers for Environmental Information}}{Sept. \textendash ~Nov. 2022}

\entrymiddle[\textbullet]
{Monitoring Trends in Tree Defoliation Due to \textit{Lymantria dispar} Outbreaks to Predict Future Hardwood Tree Mortality and Health Impacts}{\textit{NASA Ames Research Center}}{Jan. \textendash ~March 2022}

\entrymiddle[\textbullet]
{Utilizing NASA Earth Observations to Map Suitable Venus Flytrap Habitat in an Effort to Inform Conservation, Seed Banking, and Reintroduction in the Carolina Coastal Plain and Sandhills Regions}{\textit{UGA Center for Geospatial Research}}{Sept. \textendash ~Nov. 2021}

\entrymiddle[\textbullet]
{Assessing the effect of eastern hemlock (\textit{Tsuga canadensis}) decline from hemlock woolly adelgid (\textit{Adelges tsugae}) infestation on ectomycorrhizal colonization and growth of red oak (\textit{Quercus rubra}) seedlings}{\textit{Depts. of Biology, UNC Asheville and Warren Wilson College}}{May 2019 \textendash ~May 2020}

\entrymiddle[\textbullet]
{Factors contributing to reproductive success and failure in Virginia spiraea (\textit{Spiraea virginiana}), a federally threatened shrub}{\textit{Dept. of Biology, UNC Asheville}}{May 2019 \textendash ~Aug. 2020}

\entrymiddle[\textbullet]
{A CEREUS (Consortium Exchanging Research Experiences for Undergraduate Students) Approach to Assessing Ecological Responses in the Southern Appalachians to Environmental Change}{\textit{Dept. of Biology, UNC Asheville}}{Jan. 2019 \textendash ~May 2020}

\entrymiddle[\textbullet]
{Hemlock Assessment, Southern Appalachian Cooperative Ecosystems Studies Unit}{\textit{Carl Sandburg Home National Historic Site, U.S. Park Service}}{May 2019 \textendash ~May 2020}
%\entrybigwrap
%{{\textbf{Southern Appalachian Cooperative Ecosystems Studies Unit, U.S. Park Service}}{\hfill Carl Sandburg National Historic Site}}
    %{{\textsc{Role:} Research Assistant}{\hfill May 2019.\textendash May 2020}}
    %\innerlist{
        %\entry{\textsc{\underline{Principal Investigator:}} Dr. Jonathan L. \textsc{Horton}}
        %\entryextra{Assessed efficacy of biological and chemical for hemlock woolly adelgid infestation by monitoring hemlock tree canopy health, hemlock woolly adelgid infestation rates, and \textit{Laricobius} spp. predator beetle densities.}
%}
}